---
title: "Matching"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---


I want to see if it's even feasible to use matching with the AU data to test:
-	1. Reducing crop losses
-	2. Reducing unwanted fallowing/abandonment 

```{r}
library(devtools)
library(githubinstall)
library(rgdal)
library(MatchIt)
library(statsr)
library(ggplot2)

```


Get AU data (dat is spreadsheet of all AUs, au is polygons of all AUs. See "cleanup" for how these were created)
```{r setup, include = FALSE}

install_github("roopakrithi/AUdata2018", build_vignettes = F)

fl <- system.file("extdata/", package = "AUdata2018") 
dat <- read.csv(paste0(fl, "au_data.csv"))
dat <- as.data.frame(dat, stringsAsFactors = F)

au <- readOGR(dsn = paste0(fl, "au_agg.shp"), layer = "au_agg")

au <- merge(au, dat, by.x = "IDlong", 
                        by.y = "IDlong")

## calculate area variable

au$calc.area <- area(au)

## add variable for inactive (100% unused 5-yr average) vs active.
au$active <- ifelse(au$inactive.pc == 100, "inactive", "active")


## add variable: RELATIVE within-village threat: low or high
v.med.threat <- as.data.frame(tapply(au$max.threat, au$villageID, median)) # create table of village median max.threat
colnames(v.med.threat) <- "v.med.threat"
v.med.threat$ID <- c(1:7) 
au <- merge(au, v.med.threat, by.x = "villageID", by.y = "ID") # merge with AU data by villageID

# use median to create new relative threat variable
  # this is: for each village, which AUs are:
      # 1. equal to or above village-median threat ("high")
      # 2. below village-median threat ("low")
au$rel.threat <- ifelse(au$max.threat >= au$v.med.threat, "high", "low") 


# add variable "used.less" for abandoned OR declining area cultivated (10yr trend)
  # 0 = same or increased area cultivated
  # 1 = decreased area cultivated OR has not been cultivated in past 10 years or more
au$abandoned <- ifelse(au$inactive.pc == 100, 1, 0)

au$area.decline <- ifelse(au$trend.area == -1, 1, 0)

au$used.less <- ifelse((ifelse(au$inactive.pc == 100, 1, 0) +
                          ifelse(au$trend.area == -1, 1, 0))
                       >= 1, 1, 0)

table(au$used.less)


## new variable: any sort of collective activity
au$collective <- (au$monitor.3rd + au$monitor.shared)
au$collective <- ifelse(au$collective >= 1, 1, 0)

dat2 <- data.frame(au)
dat2$rel.threat.high <- ifelse(dat2$rel.threat == "high", 1, 0)

## fixing dat2, which is dat2 but with rachhiara's rel.threat.high corrected
dat2[dat2$villageID==4,c("rel.threat.high")] <- 0

## removing AUs that have been completely abandoned for more than 10 years
dat4 <- subset(dat2, inactive.pc != 100 | inactive.years <= 10)
dim(dat4)
## should have 109





```


get matchit
```{r}
#install.packages("MatchIt")
#install.packages("WhatIf")


names(dat4)
m1 <- matchit(collective ~ AU.hh + travel.time + max.threat +
              as.factor(region),
              data = dat4, method = "nearest", ratio = 1, 
              discard = "both", reestimate = T, caliper = 1 )
summary(m1)
#plot(m1, type = "jitter") 
#plot(m1, type = "hist")

df.match <- match.data(m1)
match.ca <- subset(df.match, collective == 1)
match.noca <- subset(df.match, collective == 0)

##__________________

## visualizing how well the match worked

par(mar = c(1, 3, 1, 0), mfrow = c(2, 4), oma = c(1, 0, 1, 0))
#dfmatch2 <- df.match[, c("AU.area", "AU.hh", "travel.time", "max.threat", "collective")]

for(i in 1:4) { print(tapply(dfmatch2[,i], dfmatch2$collective, summary)) }

par(mar = c(1, 3, 1, 0), mfrow = c(2, 4), oma = c(1, 0, 1, 0))
boxplot(match.ca$AU.area, main = "ca-area", ylim = c(0, 11))
boxplot(match.noca$AU.area, main = "noca-area", ylim = c(0, 11))

boxplot(match.ca$AU.hh, main = "ca-HH", ylim = c(0, 50))
boxplot(match.noca$AU.hh, main = "noca-HH", ylim = c(0, 50))

boxplot(match.ca$travel.time, main = "ca-TT", ylim = c(0, 75))
boxplot(match.noca$travel.time, main = "noca-TT", ylim = c(0, 75))

boxplot(match.ca$max.threat, main = "ca-maxthreat", ylim = c(0, 5))
boxplot(match.noca$max.threat, main = "noca-maxthreat", ylim = c(0, 5))

## __________________

# t-test: difference in proportions of used-less

inference(y=as.factor(used.less), x=as.factor(collective), data = df.match, type = "ht", null = 0, statistic = "proportion", success = "1", method = "theoretical", alternative = "twosided", sig_level = 0.05, conf_level = 0.95)


# t-test: difference in losses (max. loss to a major crop in past year)



```

TO do:
- add a quality/conditions measure. think about if this is just "high" "low", three parts, or something else. but it needs to be useful. 

- after doing this, test:
  - predictors of collectives within villages, including the "quality/conditions" variable
  - redo matching, with this included
  
