---
title: "Polygons"
author: "Roopa Krithivasan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, fig.width = 7.5, fig.height= 5}

library(sp)
library(rgdal)
library(maps)
library(maptools)
library(raster)
library(sf)
library(rgeos)
library(cleangeo)
library(plyr)

library(devtools)
library(githubinstall)
install_github("roopakrithi/AUdata2018", build_vignettes = F)

fl <- system.file("extdata/", package = "AUdata2018") 
dat <- read.csv(paste0(fl, "au_data.csv"))
dat <- as.data.frame(dat, stringsAsFactors = F)

au <- readOGR(dsn = paste0(fl, "au_agg.shp"), layer = "au_agg")

au <- merge(au, dat, by.x = "IDlong", 
                        by.y = "IDlong")

vill <- readOGR(dsn = paste0(fl, "allvillages1.shp"), layer = "allvillages1")
vill$IDs <- c(7, 6, 5, 4, 1, 2, 3)

rr <- readOGR(dsn = paste0(fl, "rivers_roads.shp"), layer = "rivers_roads")
# Symbol IDs: 0 = minor road/path; 1 = major road; 2 = minor stream; 3 = river


sett <- readOGR(dsn = paste0(fl, "settlements.shp"), layer = "settlements")

## a function to make it easier to add aux layers to all the maps
plot.sett <- function(x){
  plot(x, col = rgb(1, 1, 0, 1), border = rgb(1, 1, 0, 1), add = T)
}

plot.rr <- function(x){
  plot(subset(rr, SymbolID == 0), col = "orange", cex = 1.2, add = T)
  plot(subset(rr, SymbolID == 1), col = "orange", cex = .8, add = T)
  plot(subset(rr, SymbolID == 2), col = "cyan2", cex = 1.2, add = T)
  plot(subset(rr, SymbolID == 3), col = "cyan1", cex = .8, add = T)  
}

# using plot.sett(sett) will add settlements; plot.rr(rr) will add roads, rivers


```



## By village: median threat vs. area abandoned
(this is really sloppy but it works)
```{r}
# median value of max threat, by village
v.max.threat <- as.data.frame(tapply(au$max.threat, au$villageID, median))
colnames(v.max.threat) <- "median.threat"
v.max.threat$villageID <- rownames(v.max.threat)

## steps to get area active and inactive by village
# subset active and inactive data
active <- subset(au, inactive.pc < 100)
inactive <- subset(au, inactive.pc == 100)

# calculate area active and inactive by village using tapply on subset data
v.area.active <- as.data.frame(tapply(active$AU.area, active$villageID, sum))
colnames(v.area.active) <- "area.active"
v.area.active$villageID <- rownames(v.area.active)

v.area.inactive <- as.data.frame(tapply(inactive$AU.area, inactive$villageID, sum))
colnames(v.area.inactive) <- "area.inactive"
v.area.inactive$villageID <- rownames(v.area.inactive)

# join everything together (using "join_all" from plyr)
village.data <- plyr::join_all(list(v.max.threat, v.area.active, v.area.inactive), by = "villageID", type = "full")
village.data[is.na(village.data)] <- 0

village.data$pc.active <-  (village.data$area.active/ (village.data$area.active + village.data$area.inactive)) * 100

dev.off()
plot(village.data$pc.active ~ village.data$median.threat,  
     xlab = "median threat", ylab = "pc active", main = "Threat by village", col = "yellow", cex = 1.5, pch = 20)
text(village.data$pc.active ~ village.data$median.threat, labels = village.data$villageID, cex = .7)

```


All AUs, with scale bar and village boundaries
```{r testplot, fig.width = 7.5, fig.height= 5}

# plot all AUs ## TEST
# including a scale just for this one
### FIX so scales aren't terrible
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(1, 0, 1, 0))

for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg, col = "brown")
  plot.sett(sett)
  plot.rr(rr)
  plot(vill, border = "grey",  add = T)
  polygonsLabel(vill, labels = village.data$villageID)
  box(lty = 1)
  map.scale(ratio=F, relwidth=0.3, cex = .4, metric = T)
  if ( i == 1){
    legend("bottomright", c("Ag units", "village boundary", "settlement", "river/stream", "road"), fill = c("brown", "grey", "yellow", "cyan1", "orange"), bty = "n")
  }
}
```


A few new variables

```{r newvars}

## calculate area variable

au$calc.area <- area(au)

## add variable for inactive (100% unused 5-yr average) vs active.
au$active <- ifelse(au$inactive.pc == 100, "inactive", "active")


## add variable: RELATIVE within-village threat: low or high
v.med.threat <- as.data.frame(tapply(au$max.threat, au$villageID, median)) # create table of village median max.threat
colnames(v.med.threat) <- "v.med.threat"
v.med.threat$ID <- c(1:7) 
au <- merge(au, v.med.threat, by.x = "villageID", by.y = "ID") # merge with AU data by villageID

# use median to create new relative threat variable
  # this is: for each village, which AUs are:
      # 1. equal to or above village-median threat ("high")
      # 2. below village-median threat ("low")
au$rel.threat <- ifelse(au$max.threat >= au$v.med.threat, "high", "low") 


# add variable "used.less" for abandoned OR declining area cultivated (10yr trend)
  # 0 = same or increased area cultivated
  # 1 = decreased area cultivated OR has not been cultivated in past 10 years or more
au$abandoned <- ifelse(au$inactive.pc == 100, 1, 0)

au$area.decline <- ifelse(au$trend.area == -1, 1, 0)

au$used.less <- ifelse((ifelse(au$inactive.pc == 100, 1, 0) +
                          ifelse(au$trend.area == -1, 1, 0))
                       >= 1, 1, 0)

table(au$used.less)



## new variable: any sort of collective activity
au$collective <- (au$monitor.3rd + au$monitor.shared)
au$collective <- ifelse(au$collective >= 1, 1, 0)
```

Not perfect, but reasonable start. Don't spend too much time making this perfect. 



To add:
Rivers, major roads, settlements, and village boundaries (do this tomorrow)
maps by:


  - current use category (a few need to be modified)
   - number of users
   - live dep
  - visibility
  - more area cultivated?
  - more intensive use?
    - travel time
    - pc area cultivated
    - if abandoned, number of years
    
  
  - threat level max
    - threat level relative within village (high and low)
  - threat level by species (all together, use rgb alpha) * later
  - any collective monitoring?
  
  _____________________________________
  
  
# General characteristics 

- livelihood dependnce on agriculture
- trends in area cutlivated
- trends in cash crops 
- pc cropped (summer, 5 yr average)

```{r livdep, fig.width = 7.5, fig.height= 5}

# livelihood dependence
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, liv.dep == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Dependence on agriculture", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c(">50%", "=<50%"), fill = c("blue","white"), bty = "n")
  }
}
```



```{r pc.summer, fig.width = 7.5, fig.height= 5}
# pc cropped summer
cols <- c("#ffffff", "#e6ffe6", "#ccffcc", "#99ff99", "#66ff66", "#1aff1a", "#00e600", "#00b300",
  "#008000", "#004d00", "#003300")

layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
 plot(subset(reg, pc.cropped.summer > 0 & pc.cropped.summer <= 10 ), col = cols[1], add = T)
 plot(subset(reg, pc.cropped.summer > 10 & pc.cropped.summer <= 20 ), col = cols[2], add = T)
 plot(subset(reg, pc.cropped.summer > 20 & pc.cropped.summer <= 30 ), col = cols[3], add = T)
 plot(subset(reg, pc.cropped.summer > 30 & pc.cropped.summer <= 40 ), col = cols[4], add = T)
 plot(subset(reg, pc.cropped.summer > 40 & pc.cropped.summer <= 50 ), col = cols[5], add = T)
 plot(subset(reg, pc.cropped.summer > 50 & pc.cropped.summer <= 60 ), col = cols[6], add = T)
 plot(subset(reg, pc.cropped.summer > 60 & pc.cropped.summer <= 70 ), col = cols[7], add = T)
 plot(subset(reg, pc.cropped.summer > 70 & pc.cropped.summer <= 80 ), col = cols[8], add = T)
 plot(subset(reg, pc.cropped.summer > 80 & pc.cropped.summer <= 90 ), col = cols[9], add = T)
 plot(subset(reg, pc.cropped.summer > 90 & pc.cropped.summer <= 100 ), col = cols[10], add = T)
 plot(subset(reg, pc.cropped.summer == 0), col = "darkred", add = T)
 plot.sett(sett)
  plot.rr(rr)
 box(lty = 1, col = "grey")
  mtext("% area sown (5yr summer average)", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottomright", c("none", "1-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", 
                     "71-80", "81-90", "91-100"), fill = c("darkred", cols), 
         bty = "n", cex = .7)
  }
}


```


```{r pc.winter, fig.width = 7.5, fig.height= 5}
# pc cropped winter
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
 plot(subset(reg, pc.cropped.winter > 0 & pc.cropped.winter <= 10 ), col = cols[1], add = T)
 plot(subset(reg, pc.cropped.winter > 10 & pc.cropped.winter <= 20 ), col = cols[2], add = T)
 plot(subset(reg, pc.cropped.winter > 20 & pc.cropped.winter <= 30 ), col = cols[3], add = T)
 plot(subset(reg, pc.cropped.winter > 30 & pc.cropped.winter <= 40 ), col = cols[4], add = T)
 plot(subset(reg, pc.cropped.winter > 40 & pc.cropped.winter <= 50 ), col = cols[5], add = T)
 plot(subset(reg, pc.cropped.winter > 50 & pc.cropped.winter <= 60 ), col = cols[6], add = T)
 plot(subset(reg, pc.cropped.winter > 60 & pc.cropped.winter <= 70 ), col = cols[7], add = T)
 plot(subset(reg, pc.cropped.winter > 70 & pc.cropped.winter <= 80 ), col = cols[8], add = T)
 plot(subset(reg, pc.cropped.winter > 80 & pc.cropped.winter <= 90 ), col = cols[9], add = T)
 plot(subset(reg, pc.cropped.winter > 90 & pc.cropped.winter <= 100 ), col = cols[10], add = T)
  plot(subset(reg, pc.cropped.winter == 0), col = "darkred", add = T)
  plot.sett(sett)
  plot.rr(rr)
 box(lty = 1, col = "grey")
  mtext("% area sown (5yr winter average)", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottomright", c("none", "1-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", 
                     "71-80", "81-90", "91-100"), fill = c("darkred", cols), 
         bty = "n", cex = .7)
  }
}



```


```{r trend.area, fig.width = 7.5, fig.height= 5}
## more area cultivated now than 10 years ago
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, trend.area == 1), col = "green", add = T)
  plot(subset(reg, trend.area == 0), col = "grey", add = T)
  plot(subset(reg, trend.area == -1), col = "red", add = T)
  plot(subset(reg, inactive.years > 10 & inactive.pc == 100), col = "darkred", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Area sown now vs. 10 yrs ago", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottomright", c("Increase", "No change", "Decrease", "inactive >10yrs"), fill = c("green", "grey", "red", "darkred"), bty = "n")
  }
}

```


```{r trend.cash.crops, fig.width = 7.5, fig.height= 5}
# More cash crops cultivated now than 10 years ago
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, trend.cash.crops == 1), col = "green", add = T)
  plot(subset(reg, trend.cash.crops == -1), col = "red", add = T)
  plot(subset(reg, trend.cash.crops == 0), col = "grey", add = T)
  plot(subset(reg, inactive.years > 10 & inactive.pc == 100), col = "darkred", add = T)
  plot.sett(sett)
  plot.rr(rr)
  #plot(subset(reg, type == "unused"), col = "black", add = T)
 box(lty = 1, col = "grey")
  mtext("Cash crop cultivation now vs. 10 yrs ago", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottomright", c("Increase", "No change", "Decrease", "inactive >10yrs"), fill = c("green", "grey", "red", "darkred"), bty = "n")
  }
}

```
  
# Borders and visibility

```{r borders.settl, fig.width = 7.5, fig.height= 5}
# Borders settlement
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, borders.settl == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Borders settlement", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("y", "n"), fill = c("blue","white"), bty = "n")
  }
 }


```


```{r borders.water, fig.width = 7.5, fig.height= 5}
# Borders water
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, borders.water == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Borders water", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("y", "n"), fill = c("blue","white"), bty = "n")
  }
 }

```


```{r borders.forest, fig.width = 7.5, fig.height= 5}
# Borders forest
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, borders.forest == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Borders forest", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("y", "n"), fill = c("blue","white"), bty = "n")
  }
 }


```


```{r vis.settl, fig.width = 7.5, fig.height= 5}

# Majority visible from settlement
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, vis.settl == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Majority visible from settlement", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("y", "n"), fill = c("blue","white"), bty = "n")
  }
}


```

```{r vis.any, fig.width = 7.5, fig.height= 5}

# Majority visible from settlement or area of high traffic
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, vis.any == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Majority visible from settlement or high-traffic area", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("y", "n"), fill = c("blue","white"), bty = "n")
  }
 }

```

# Travel time

```{r travel.time, fig.width = 7.5, fig.height= 5}
# travel time
cols <- c("#ffffff", "#e6e6ff", "#b3b3ff", "#8080ff", "#4d4dff", "#1a1aff", "#0000b3","#000099", "#00004d", "#00001a")

layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
plot(subset(reg, travel.time == 0), col = cols[1], add = T)
 plot(subset(reg, travel.time > 0 & travel.time <= 2 ), col = cols[2], add = T)
 plot(subset(reg, travel.time > 3 & travel.time <= 5 ), col = cols[3], add = T)
 plot(subset(reg, travel.time > 5 & travel.time <= 10 ), col = cols[4], add = T)
 plot(subset(reg, travel.time > 10 & travel.time <= 15 ), col = cols[5], add = T)
 plot(subset(reg, travel.time > 15 & travel.time <= 20 ), col = cols[6], add = T)
 plot(subset(reg, travel.time > 20 & travel.time <= 30 ), col = cols[7], add = T)
 plot(subset(reg, travel.time > 30 & travel.time <= 45 ), col = cols[8], add = T)
 plot(subset(reg, travel.time > 45 & travel.time <= 60 ), col = cols[9], add = T)
 plot(subset(reg, travel.time > 60 & travel.time <= 80 ), col = cols[10], add = T)
  plot.sett(sett)
  plot.rr(rr)
 box(lty = 1, col = "grey")
  mtext("Average travel time (minutes)", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottomright", c("0", "1-2", "3-5", "6-10", "11-15", "16-20", "21-30", "31-45", 
                     "46-60", "61-80"), fill = c(cols), 
         bty = "n", cex = .7)
  }
}

layout(matrix(1,1))
par(mar = c(5,1,1,1), oma = c(1, 1, 1, 1))
hist(dat$travel.time, breaks = 15, main = "travel time", xlab = "minutes")

boxplot(au$travel.time ~ au$active, main = "travel time", xlab = "minutes")
tapply(au$travel.time, au$active, median)

 
```
  
  
# Threat level
```{r monkey.theat, fig.width = 7.5, fig.height= 5}

#MONKEY
cols <- sapply(1:5, function(x){
  rgb(1, 0, 0, (2.5^x)/100)
})
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
      plot(reg)
      for(j in 1:5){
      plot(subset(reg, monkey.threat == j), col = cols[j], add = T)
      }
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Monkey damage/loss threat", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottom", c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols), bty = "n")
  }
}

```


```{r boar.threat, fig.width = 7.5, fig.height= 5}
#BOAR
cols <- sapply(1:5, function(x){
  rgb(1, 0, 0, (2.5^x)/100)
})
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
      plot(reg)
      for(j in 1:5){
      plot(subset(reg, boar.threat == j), col = cols[j], add = T)
      }
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Boar damage/loss threat", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottom", c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols), bty = "n")
  }
}
```


```{r ung.threat, fig.width = 7.5, fig.height= 5}

#UNGULATE
cols <- sapply(1:5, function(x){
  rgb(1, 0, 0, (2.5^x)/100)
})
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
      plot(reg)
      for(j in 1:5){
      plot(subset(reg, ung.threat == j), col = cols[j], add = T)
      }
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Ungulate damage/loss threat", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottomright", c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols), bty = "n")
  }
}


```

```{r max.threat, fig.width = 7.5, fig.height= 5}
# Overall threat levels
cols <- sapply(1:5, function(x){
  rgb(1, 0, 0, (2.5^x)/100)
})
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
      plot(reg)
      for(j in 1:5){
      plot(subset(reg, max.threat == j), col = cols[j], add = T)
      }
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Maximum wildlife damage/loss threat", side = 3, outer = TRUE)
  if ( i == 1){
  legend("bottomright", c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols), bty = "n")
  }
}


```
  
# Village relative threat
```{r rel.threat, fig.width = 7.5, fig.height= 5}
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, rel.threat == "high"), col = "darkred", add = T)
  plot(subset(reg, rel.threat == "low"), col = "orange", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("Within-village relative threat", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("high", "low"), fill = c("darkred","orange"), bty = "n")
  }
}
```



# Monitoring and protection
```{r 3rd.party, fig.width = 7.5, fig.height= 5}
# 3rd PARTY
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, monitor.3rd == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("3rd party monitoring (any crop in past 2yrs)", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c(">50%", "=<50%"), fill = c("blue","white"), bty = "n")
  }
}


```


```{r monitor.shared, fig.width = 7.5, fig.height= 5}

# ROTATIONAL/SHARED MONITORING
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, monitor.shared == 1), col = "blue", add = T)
  plot.sett(sett)
  plot.rr(rr)
  box(lty = 1, col = "grey")
  mtext("shared monitoring (any crop in past 2yrs", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("Y", "N"), fill = c("blue","white"), bty = "n")
  }
 }

```
  
I want relative within-village threat
- find median threat value for each village (tapply)
- anything assign "high" and "low" based on median
- map

bivariate tables of:
- village-level threat vs use category (abandoned, under 50% used, >50% used)
- travel distance vs. use category (maybe as x-y plots)
  
  
## By village: median threat vs. area abandoned
(this is really sloppy but it works)
```{r}
# median value of max threat, by village
v.max.threat <- as.data.frame(tapply(au$max.threat, au$villageID, median))
colnames(v.max.threat) <- "median.threat"
v.max.threat$villageID <- rownames(v.max.threat)

## steps to get area active and inactive by village
# subset active and inactive data
active <- subset(au, inactive.pc < 100)
inactive <- subset(au, inactive.pc == 100)

# calculate area active and inactive by village using tapply on subset data
v.area.active <- as.data.frame(tapply(active$AU.area, active$villageID, sum))
colnames(v.area.active) <- "area.active"
v.area.active$villageID <- rownames(v.area.active)

v.area.inactive <- as.data.frame(tapply(inactive$AU.area, inactive$villageID, sum))
colnames(v.area.inactive) <- "area.inactive"
v.area.inactive$villageID <- rownames(v.area.inactive)

# join everything together (using "join_all" from plyr)
village.data <- plyr::join_all(list(v.max.threat, v.area.active, v.area.inactive), by = "villageID", type = "full")
village.data[is.na(village.data)] <- 0

village.data$pc.active <-  (village.data$area.active/ (village.data$area.active + village.data$area.inactive)) * 100

dev.off()
plot(village.data$pc.active ~ village.data$median.threat,  
     xlab = "median threat", ylab = "pc active", main = "Threat by village", col = "yellow", cex = 1.5, pch = 20)
text(village.data$pc.active ~ village.data$median.threat, labels = village.data$villageID, cex = .7)

```

  
  
  
  
  
  
  
  
  
  
  
JUNK

```{r junk1, eval = F}
proj4string(au)

att <- data.frame(au)

vnames <- c("Gr", "BB", "Dh", "Sp", "Ra", "Su", "Ro")

layout(matrix(c(1,1), 1, 1))
par(mar = c(1, 1, 1, 1), oma = c(2, 3, 2, 0))
barplot(tapply(att$calc, att$villageID, function(x){sum(x)/1000}), las = 1,
               names.arg = c("Gr", "BB", "Dh", "Sp", "Ra", "Su", "Ro"))

```

```{r junk2, eval = F}
### all vis combined: this works but it's hella ugly.
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
 for(x in 1:length(au)){
    plot(au[x,], col = rgb(
      .5*(slot(au, "data")[x,17]) + .5*(slot(au, "data")[x,18]), 
      slot(au, "data")[x,18], 
      slot(au, "data")[x,19], 
      1), add = T)
 }
  box(lty = 1, col = "grey")
  mtext("Borders settlement/forest/water", side = 3, outer = TRUE)
  if ( i == 1){
    legend("bottomright", c("settlement", "forest", "water"), fill = c("red","yellow", "blue"), 
           pt.cex = 3, bty = "n")
  }
}

### DOESN'T WORK
layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
      plot(reg)
      for(j in 1:5){
      plot(subset(reg, monkey.threat == j), col = cols_monkey[j], add = T)
      plot(subset(reg, boar.threat == j), col = cols_boar[j], add = T)
      plot(subset(reg, ung.threat == j), col = cols_ung[j], add = T)
      }
  box(lty = 1, col = "grey")
  mtext("Maximum wildlife damage/loss threat", side = 3, outer = TRUE)
  if ( i == 1){
    legend(x = 76.927, y = 31.975, c("", "", "", "", ""), fill = rev(cols_monkey), bty = "n")
    legend(x = 76.929, y = 31.975, c("", "", "", "", ""), fill = rev(cols_boar), bty = "n")
    legend(x = 76.931, y = 31.975, c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols_ung), bty = "n")
  }
   text("M B U", x = 76.9318, y = 31.975, cex = .85)  
}

## By species THIS NEEDS WORK
cols_monkey <- sapply(1:5, function(x){
  rgb(1, 0, 0, (2.5^x)/100)
})
cols_boar <- sapply(1:5, function(x){
  rgb(0, 0, 1, (2.5^x)/100)
})
cols_ung <- sapply(1:5, function(x){
  rgb(1, 1, 0, (2.5^x)/100)
})


layout(matrix(c(1,2,1,3), 2, 2, byrow = T), widths = c(1.4,1))
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 3, 0))
for(i in 1:3){
  reg <- au[au$region == i, ]
      plot(reg)
      for(j in 1:5){
      plot(subset(reg, monkey_thr == j), col = cols_monkey[j], add = T)
      plot(subset(reg, boar_threa == j), col = cols_boar[j], add = T)
      plot(subset(reg, ung_threat == j), col = cols_ung[j], add = T)
      }
  box(lty = 1, col = "grey")
  mtext("Maximum wildlife damage/loss threat", side = 3, outer = TRUE)
  if ( i == 1){
    legend(x = 76.927, y = 31.975, c("", "", "", "", ""), fill = rev(cols_monkey), bty = "n")
    legend(x = 76.929, y = 31.975, c("", "", "", "", ""), fill = rev(cols_boar), bty = "n")
    legend(x = 76.931, y = 31.975, c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols_ung), bty = "n")
  }
   text("M B U", x = 76.9318, y = 31.975, cex = .85)  
}

```

  
  
  I know I shouldnt but just messing around with some analyses here here:

1. hyp: AUs with higher exposure to wildlife within a village are more likely to be farmed less or abandoned.  
```{r}

# A qiuck map, red is high relative threat
for(i in 1:3){
  reg <- au[au$region == i, ]
  plot(reg)
  plot(subset(reg, rel.threat == "high"), col = "red", add = T)
}


### test using chi-squared, to start, 

dat2 <- data.frame(au)
tbl <- table(dat2$used.less,dat2$rel.threat)

tbl = tbl[1:2, ]
chisq.test(tbl)

```
OK, this looks like there might be something there. 


2. this relationship holds even when controlling for a few significant factors (the main one I'm worried about is convenience... are these abandoned just becuase they're far away?)
### note: WILDLIFE EXPOSURE ISN'T A SIG PREDICTOR UNLESS I CONTROL FOR VILLAGES... WHY?. becuase village variablity, even if it's not significant for 5 of the villages, is accounting for some of the variablity. these are largely village level effects. talk to tim about this. 
```{r}
dev.off()

dat2$rel.threat.high <- ifelse(dat2$rel.threat == "high", 1, 0)

lm1 <- lm(used.less ~ rel.threat.high, dat2)
summary(lm1)
plot(used.less ~ rel.threat.high, dat2)


lm2 <- lm(used.less ~ tt2 + rel.threat.high, dat2)
summary(lm2)

lm3 <- glm(used.less ~ tt2 + rel.threat.high + vis.settl, dat2, family = binomial)
summary(lm3)

lm4 <- glm(used.less ~ rel.threat.high + vis.any, dat2, family = "binomial")
summary(lm4)


lm5 <- glm(used.less ~ travel.time + vis.any, data = dat2, family = binomial)
summary(lm5)

lm6 <- lm(pc.cropped.summer ~ tt2 + vis.any + rel.threat.high, dat2)
summary(lm6)

lm7 <- glm(used.less ~  max.threat, dat2, family = binomial)
summary(lm7)

lm8 <- glm(used.less ~  max.threat + as.factor(villageID), dat2, family = binomial)
summary(lm8)

lm9 <- glm(used.less ~  tt2 + vis.settl + rel.threat.high + as.factor(villageID), dat2, family = binomial)
summary(lm9)

lm9 <- glm(used.less ~  travel.time + tt2, dat2, family = binomial)
summary(lm9)

```
- lm and lm2: Even when cotrolling for average travel time to the AU (which should be a good proxy for the convenience of farming an AU; more distant == less convenient == used less); relative threat is a significant predictor of declining use
- lm3: however, if you add a term for visibility; rel.threat is no longer significant, and the best predictor is if it's visible from the settlement or not. that is, if it's visible, that significantly decreases the odds that it's used less.
- that is, defensibility is as important, if not MORE important, than exposure. people want to farm where they know they can protect


### proportions
```{r}
## do more exposed fields have more abandonment

# CI for high exposure fields that are used less
prop.test(41, 80, conf.level = .90)
# 90 percent confidence interval: 0.4156188 0.6085087

# CI for low exposure fields that are used less
prop.test(11, 41, conf.level = .90) 
# 90 percent confidence interval: 0.161554 0.406672

table(dat2$used.less, dat2$rel.threat.high)
barplot(table(dat2$used.less, dat2$rel.threat.high))

# log odds of less use/abandonment predicted by relative (within-village) exposure, and controlling for village
glm1 <- glm(dat2$used.less ~ dat2$rel.threat.high + as.factor(dat2$villageID), family = "binomial")
summary(glm1)
## suggests threat matters

# same as above but adding travel time
glm2 <- glm(dat2$used.less ~ dat2$rel.threat.high + dat2$travel.time +
              as.factor(dat2$villageID), family = "binomial")
summary(glm2)
# relationship still holds

# what about if using squared travel time instead
glm3 <- glm(dat2$used.less ~ dat2$rel.threat.high + dat2$tt2 +
              as.factor(dat2$villageID), family = "binomial")
summary(glm3)
# threat is still a sig predictor 

# what about if using visibility instead
glm3 <- glm(dat2$used.less ~ dat2$rel.threat.high + dat2$vis.any +
              as.factor(dat2$villageID), family = "binomial")
summary(glm3)
# threat is still a sig predictor, but visibility is a bigger predictor 

glm4 <- glm(dat2$used.less ~ dat2$rel.threat.high + dat2$borders.forest +
              as.factor(dat2$villageID), family = "binomial")
summary(glm4)

glm5 <- glm(dat2$used.less ~ dat2$rel.threat.high + dat2$borders.forest + 
              as.factor(dat2$villageID), family = "binomial")


```




MAPS FOR PRESENTATION:

1. VILLAGES
```{r}
dev.off()
par(mar = c(0, 0, 0, 0), mfrow = c(2, 4), oma = c(1, 0, 1, 0))

for(i in 1:7){
  plot(vill[vill$IDs == i,], col = "grey", border = "grey", main = i, line= -1.5, cex.main = 2)
  plot(au[au$villageID == i, ], col = "brown3", border = "brown", add = T)
  plot.sett(sett)
  plot.rr(rr)
  #plot(vill, border = "grey",  add = T)
  box(lty = 1, col = "lightgrey")

  map.scale(ratio=F, relwidth=0.5, cex = .5, metric = T)
}

plot(0, 0, type='n', bty='n', xaxt='n', yaxt='n')
    legend("left", c("Ag units", "village boundary", "settlement", "river/stream", "road"), fill = c("brown3", "grey", "yellow", "cyan1", "orange"), bty = "n", cex = 1.5)

```

Districts in study
```{r}
dev.off()
adm <- readOGR("/Users/roopa 1/Desktop/Himachal_data/UsefulShapefiles/hp/hp.shp")

plot(adm, col = "lightgrey", border = "black")
plot(adm[c(99, 100, 112), ], add = T, col = c("aquamarine", "darkcyan", "chocolate2"), border = "black")
legend("bottomright", c("Padhar", "Palampur", "Jaisinghpur"), fill = c("chocolate2", "darkcyan", "aquamarine"), bty = "n", cex = 1)


## HP map
dev.off()
#ind <- readRDS("/Users/roopa 1/Dropbox/Clark/2017-FALL/Rclass/Assignment1a/india1/inst/extdata/IND_adm3.rds")

#plot(ind)

```

Maps for just for one village
  include:
  - pc cultivated (three year average, summer)
  - visible from settlement (y/n)
  - travel time
  - # Households
  - rel. wildlife threat
  - Collective monitoring practiced (y/n)
 
  - [time permitting] primary crops (summer, winter)
  
  
```{r}
dev.off()
par(mar = c(0, 0, .5, 0), mfrow = c(2, 4), oma = c(1, 0, 1, 0))

## fill in village ID and corresponding units for village of interest
villID <- 2
units <- c(28:49)

# Village features
  reg <- au[units,]
  plot(vill[vill$IDs == villID,], main = "Village features", line= -1.5, cex.main = 1)
  plot(reg, col = "lightgreen", add = T)
  #plot(reg, col = "lightgreen")
  plot.sett(sett)
  plot.rr(rr)
  plot(vill, border = "grey",  add = T)
  #polygonsLabel(vill, labels = village.data$villageID)
  #box(lty = 1)
  #map.scale(ratio=F, relwidth=0.3, cex = .4, metric = T)
legend("bottomright", c("Ag units", "village boundary", "settlement", "river/stream", "road"), fill = c("lightgreen", "grey", "yellow", "cyan1", "orange"), bty = "n", cex = .7, y.intersp=.7)


# PC CULTIVATED
cols <- c("#ffffff", "#e6ffe6", "#ccffcc", "#99ff99", "#66ff66", "#1aff1a", "#00e600", "#00b300",
  "#008000", "#004d00", "#003300")

  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "% area sown \n (5yr winter ave.)", line= -1.8, 
       cex.main = 1)
  plot(reg, add = T)
plot(subset(reg, pc.cropped.winter > 0 & pc.cropped.winter <= 10 ), col = cols[1], add = T)
 plot(subset(reg, pc.cropped.winter > 10 & pc.cropped.winter <= 20 ), col = cols[2], add = T)
 plot(subset(reg, pc.cropped.winter > 20 & pc.cropped.winter <= 30 ), col = cols[3], add = T)
 plot(subset(reg, pc.cropped.winter > 30 & pc.cropped.winter <= 40 ), col = cols[4], add = T)
 plot(subset(reg, pc.cropped.winter > 40 & pc.cropped.winter <= 50 ), col = cols[5], add = T)
 plot(subset(reg, pc.cropped.winter > 50 & pc.cropped.winter <= 60 ), col = cols[6], add = T)
 plot(subset(reg, pc.cropped.winter > 60 & pc.cropped.winter <= 70 ), col = cols[7], add = T)
 plot(subset(reg, pc.cropped.winter > 70 & pc.cropped.winter <= 80 ), col = cols[8], add = T)
 plot(subset(reg, pc.cropped.winter > 80 & pc.cropped.winter <= 90 ), col = cols[9], add = T)
 plot(subset(reg, pc.cropped.winter > 90 & pc.cropped.winter <= 100 ), col = cols[10], add = T)
  plot(subset(reg, pc.cropped.winter == 0), col = "darkred", add = T)

  legend("bottomright", c("none", "1-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", 
                     "71-80", "81-90", "91-100"), fill = c("darkred", cols), 
         bty = "n", cex = .7, y.intersp=.7)


# Majority visible from settlement
  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "Visible from \n settlement", line= -1.8, cex.main = 1)
  plot(reg, add = T)
  plot(subset(reg, vis.settl == 1), col = "blue", add = T)
  #box(lty = 1, col = "grey")
legend("bottomright", c("Y", "N"), fill = c("blue","white"), bty = "n", cex = .7, y.intersp=.7)



# TRAVEL TIME
cols <- c("#ffffff", "#e6e6ff", "#b3b3ff", "#8080ff", "#4d4dff", "#1a1aff", "#0000b3","#000099", "#00004d", "#00001a")

  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "Travel time (mins)", line= -1.5, cex.main = 1)
  plot(reg, add = T)
plot(subset(reg, travel.time == 0), col = cols[1], add = T)
 plot(subset(reg, travel.time > 0 & travel.time <= 2 ), col = cols[2], add = T)
 plot(subset(reg, travel.time > 3 & travel.time <= 5 ), col = cols[3], add = T)
 plot(subset(reg, travel.time > 5 & travel.time <= 10 ), col = cols[4], add = T)
 plot(subset(reg, travel.time > 10 & travel.time <= 15 ), col = cols[5], add = T)
 plot(subset(reg, travel.time > 15 & travel.time <= 20 ), col = cols[6], add = T)
 plot(subset(reg, travel.time > 20 & travel.time <= 30 ), col = cols[7], add = T)
 plot(subset(reg, travel.time > 30 & travel.time <= 45 ), col = cols[8], add = T)
 plot(subset(reg, travel.time > 45 & travel.time <= 60 ), col = cols[9], add = T)
 plot(subset(reg, travel.time > 60 & travel.time <= 80 ), col = cols[10], add = T)

  legend("bottomright", c("0", "1-2", "3-5", "6-10", "11-15", "16-20", "21-30", "31-45", 
                     "46-60", "61-80"), fill = c(cols), 
         bty = "n", cex = .7, y.intersp=.7)


  
# Managing HHs
cols <- c("#ffffff", "#e6e6ff", "#b3b3ff", "#8080ff", "#4d4dff", "#1a1aff", "#0000b3","#000099", "#00004d", "#00001a")

  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "# Managing \n households", line= -1.8, cex.main = 1)
  plot(reg, add = T)
plot(subset(reg, travel.time == 0), col = cols[1], add = T)
 plot(subset(reg, AU.hh > 0 & AU.hh <= 10 ), col = cols[2], add = T)
 plot(subset(reg, AU.hh > 10 & AU.hh <= 20 ), col = cols[3], add = T)
 plot(subset(reg, AU.hh > 20 & AU.hh <= 30 ), col = cols[4], add = T)
 plot(subset(reg, AU.hh > 30 & AU.hh <= 50 ), col = cols[5], add = T)

  legend("bottomright", c("1-10", "10-20", "21-30", "31-40"), fill = c(cols[c(2, 3, 4, 5)]), 
         bty = "n", cex = .7, y.intersp=.7)

    
# CROP RAIDING THREAT
cols <- sapply(1:5, function(x){
  rgb(1, 0, 0, (2.5^x)/100)
})

  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "Crop raiding \n relative threat", line= -1.8, 
         cex.main = 1)
  plot(reg, add = T)
      for(j in 1:5){
      plot(subset(reg, max.threat == j), col = cols[j], add = T)
      }
  # box(lty = 1, col = "grey")
  legend("bottomright", c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols), bty = "n", cex = .7, y.intersp=.7)

  
# 3rd PARTY monitoring
  reg <- au[units,]
  plot(vill[vill$IDs == villID,],border = "grey", main = "3rd party \n monitoring", line= -1.8, cex.main = 1)
  plot(reg, add = T)
  plot(subset(reg, monitor.3rd == 1), col = "blue", add = T)
  #plot.sett(sett)
  #plot.rr(rr)
  #box(lty = 1, col = "grey")

legend("bottomright", c("Y", "N"), fill = c("blue","white"), bty = "n", cex = .7, y.intersp=.7)

# rotational monitoring
  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "Rotational \n monitoring", line= -1.8, cex.main = 1)
  plot(reg, add = T)
  plot(subset(reg, monitor.shared == 1), col = "blue", add = T)

    legend("bottomright", c("Y", "N"), fill = c("blue","white"), bty = "n", cex = .7, y.intersp=.7)
  map.scale(ratio=F, relwidth=0.38, cex = .7, metric = T)
 




```
  

Districts in study
```{r}
dev.off()
adm <- readOGR("/Users/roopa 1/Desktop/Himachal_data/UsefulShapefiles/hp/hp.shp")

plot(adm, col = "lightgrey", border = "black")
plot(adm[c(99, 100, 112), ], add = T, col = c("aquamarine", "darkcyan", "chocolate2"), border = "black")
legend("bottomright", c("Padhar", "Palampur", "Jaisinghpur"), fill = c("chocolate2", "darkcyan", "aquamarine"), bty = "n", cex = 1)


## HP map
dev.off()
#ind <- readRDS("/Users/roopa 1/Dropbox/Clark/2017-FALL/Rclass/Assignment1a/india1/inst/extdata/IND_adm3.rds")

#plot(ind)

```


Subsample  
```{r}
dev.off()
par(mar = c(0, 0, .5, 0), mfrow = c(2, 3), oma = c(1, 0, -.1, 0))

## fill in village ID and corresponding units for village of interest
villID <- 2
units <- c(28:49)


# PC CULTIVATED
cols <- c("#ffffff", "#e6ffe6", "#ccffcc", "#99ff99", "#66ff66", "#1aff1a", "#00e600", "#00b300",
  "#008000", "#004d00", "#003300")

  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "(b) % area sown \n (5yr winter ave.)", line= -2.45, 
       cex.main = 1)
  plot(reg, add = T)
plot(subset(reg, pc.cropped.winter > 0 & pc.cropped.winter <= 10 ), col = cols[1], add = T)
 plot(subset(reg, pc.cropped.winter > 10 & pc.cropped.winter <= 20 ), col = cols[2], add = T)
 plot(subset(reg, pc.cropped.winter > 20 & pc.cropped.winter <= 30 ), col = cols[3], add = T)
 plot(subset(reg, pc.cropped.winter > 30 & pc.cropped.winter <= 40 ), col = cols[4], add = T)
 plot(subset(reg, pc.cropped.winter > 40 & pc.cropped.winter <= 50 ), col = cols[5], add = T)
 plot(subset(reg, pc.cropped.winter > 50 & pc.cropped.winter <= 60 ), col = cols[6], add = T)
 plot(subset(reg, pc.cropped.winter > 60 & pc.cropped.winter <= 70 ), col = cols[7], add = T)
 plot(subset(reg, pc.cropped.winter > 70 & pc.cropped.winter <= 80 ), col = cols[8], add = T)
 plot(subset(reg, pc.cropped.winter > 80 & pc.cropped.winter <= 90 ), col = cols[9], add = T)
 plot(subset(reg, pc.cropped.winter > 90 & pc.cropped.winter <= 100 ), col = cols[10], add = T)
  plot(subset(reg, pc.cropped.winter == 0), col = "darkred", add = T)

  legend("bottomright", c("none", "", "", "", "", "41-50", "", "", 
                     "", "", "91-100"), fill = c("darkred", cols), border = "white",
         bty = "n", cex = .8, y.intersp=.5)

# CROP RAIDING THREAT
cols <- sapply(1:5, function(x){
  rgb(1, 0, 0, (2.5^x)/100)
})

  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "(c) Crop raiding \n relative threat", line= -2.45, 
         cex.main = 1)
  plot(reg, add = T)
      for(j in 1:5){
      plot(subset(reg, max.threat == j), col = cols[j], add = T)
      }
  # box(lty = 1, col = "grey")
  legend("bottomright", c("severe", "high", "moderate", "low", "v. low"), fill = rev(cols), bty = "n", cex = 1, y.intersp=.7, border = "white")
  map.scale(ratio=F, relwidth=0.2, cex = .7, metric = T)  
  
# TRAVEL TIME
cols <- c("#ffffff", "#e6e6ff", "#b3b3ff", "#8080ff", "#4d4dff", "#1a1aff", "#0000b3","#000099", "#00004d", "#00001a")

  reg <- au[units,]
  plot(vill[vill$IDs == villID,], border = "grey", main = "(d) Travel time (mins)", line= -1.8, cex.main = 1)
  plot(reg, add = T)
plot(subset(reg, travel.time == 0), col = cols[1], add = T)
 plot(subset(reg, travel.time > 0 & travel.time <= 2 ), col = cols[2], add = T)
 plot(subset(reg, travel.time > 3 & travel.time <= 5 ), col = cols[3], add = T)
 plot(subset(reg, travel.time > 5 & travel.time <= 10 ), col = cols[4], add = T)
 plot(subset(reg, travel.time > 10 & travel.time <= 15 ), col = cols[5], add = T)
 plot(subset(reg, travel.time > 15 & travel.time <= 20 ), col = cols[6], add = T)
 plot(subset(reg, travel.time > 20 & travel.time <= 30 ), col = cols[7], add = T)
 plot(subset(reg, travel.time > 30 & travel.time <= 45 ), col = cols[8], add = T)
 plot(subset(reg, travel.time > 45 & travel.time <= 60 ), col = cols[9], add = T)
 plot(subset(reg, travel.time > 60 & travel.time <= 80 ), col = cols[10], add = T)

  legend("bottomright", c("0", "1-2", "3-5", "6-10", "11-15", "16-20", "21-30", "31-45", 
                     "46-60", "61-80"), fill = c(cols), 
         bty = "n", cex = .8, y.intersp=.7, border = "white")



 


```
